Fourmile Calibrations and Output

### 2023-05-03 38HRU_model/fourmile_model_outputs.Rmd
added Q!

```{echo = FALSE, message = FALSE, warning = FALSE, include = F}

#pull in all filenames with composite
filenames <- list.files('.', pattern=".csv", full.names=TRUE)

@@

name <- levels(burn_params$params)

lapply(name, plot_burnparams)

@@

```{r hydrographs, echo = F}
flow <- read_csv('discharge_all.csv') %>%
  replace(.==-9999, NA)

@@

q_ensemble <- ggplot(ensem_pivot, aes(date, q_m3s, color = cal_run)) +
  geom_line() +
  scale_color_manual(name="cal_run", values=c('obs'='black',
                                            "grid_ensemble"="maroon",
                                            "statn_ensemble"="darkturquoise",
                                            "grid_all"="purple1",
                                            "statn_all"='springgreen4',
                                            "all_ensemble" = "orange")) +
  geom_line(data = bouldcr, aes(date, bouldcr/10), color = 'darkgrey') +
  scale_y_continuous(name = 'Q_m3s',
                    sec.axis = sec_axis(~.*10, name='BoulderCr_cms')) +
  theme_bw()

ggplotly(q_ensemble) %>%
  add_lines(data=bouldcr, x=~date, y=~bouldcr, colors=NULL, yaxis="y2",
              inherit=FALSE, showlegend = FALSE) %>%
  layout(yaxis2 = list(overlaying = "y", side = "right",
                       color = 'darkgray',
                       title = "BoulderCr_cms"),
         legend = list(x = 1.1, y = 0.95))

@@

# Catchment results

## Precip

```{r catch precip, echo = F}
setwd("/Users/megansears/Documents/Repos/fourmile/catchment_output")

statn <- read_csv('statnall.csv')
grid <- read_csv('gridall.csv')

grid <- grid %>% mutate(site = 'grid')
statn <- statn %>% mutate(site = 'statn')

catchment <- bind_rows(grid, statn) %>%
  mutate(year = as.factor(year(time))) %>%
  group_by(year, site) %>%
  mutate(cumulative_p = cumsum(precip))

#plot cumulative precip by year
plot_cumprecip <- function(calyear) {
  {catchment %>%
    filter(year == calyear) %>%
    ggplot(aes(x = time,
               y = cumulative_p, color = site)) +
    geom_line(size=1) +
    ggtitle(calyear) +
    ylab('Cumulative precip (mm)') +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust=1))} %>%
    ggplotly()
}

name <- levels(catchment$year)

precip_plots <- lapply(name, plot_cumprecip)

htmltools::tagList(precip_plots)

precip_plots

## total P
max_cumulativep <- catchment %>%
  group_by(year, site) %>%
  summarize(total_cumulativep = max(cumulative_p))

ggplot(max_cumulativep, aes(x=year, y=total_cumulativep, color=site)) +
  geom_point(size=3) +
  ggtitle('Total cumulative precip (mm) by year')

## Tmean

```{r tmean catch, echo = F}
## tmean
tmean <- catchment %>%
  group_by(year, site) %>%
  summarize(tmean = mean(tmean)) %>%
  ggplot(aes(x = year, y=tmean, color = site)) +
  geom_point(size=3) +
  ggtitle('Average temp by year')

tmean

## RD and RG

```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"}

gw_grid <- read_csv(here('catchment_output/gridall_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid')

gw_statn <- read_csv(here('catchment_output/statnall_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn')

gw <- bind_rows(gw_grid, gw_statn) %>%
  mutate(year = year(time)) %>%
  rename(date = time)

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRD1_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RD1') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRD2_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RD2') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRG1_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RG1') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=catchmentRG2_w), size =1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('RG2') +
  theme(text = element_text(size = 20))

gw <- gw %>%
  group_by(year, source) %>%
  mutate(RD1cumsum = cumsum(catchmentRD1_w),
         RD2cumsum = cumsum(catchmentRD2_w),
         RG1cumsum = cumsum(catchmentRG1_w),
         RG2cumsum = cumsum(catchmentRG2_w))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD1cumsum), size =1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RD1') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RD2cumsum), size = 1) +
  facet_wrap(~year, scales = 'free', ncol=2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RD2') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG1cumsum), size  = 1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RG1') +
  theme(text = element_text(size = 20))

ggplot(gw, aes(x=date, color = source)) +
  geom_line(aes(y=RG2cumsum), size =1) +
  facet_wrap(~year, scales = 'free', ncol = 2) +
  scale_x_date(labels = date_format("%b")) +
  ggtitle('Cumulative RG2') +
  theme(text = element_text(size = 20))

```{r rd and rg sums, echo = F, fig.width = 22, fig.asp = 1.5, out.width = "100%"}

##################
# all 4 with facets

ggplot(gw, aes(x=date)) +
  geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) +
  geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) +
  geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) +
  geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) +
  scale_x_date(labels = date_format("%b")) +
  facet_wrap(~year + source, scales = 'free_x', ncol=2) +
  ggtitle('Cumulative RD and RG') +
  theme(text = element_text(size = 24))

```{r gw boxplot, echo = F}

gw_maxcumsum <- gw %>%
  group_by(source, year) %>%
  summarize(yr_max_RD1 = max(RD1cumsum),
            yr_max_RD2 = max(RD2cumsum),
            yr_max_RG1 = max(RG1cumsum),
            yr_max_RG2 = max(RG2cumsum)) %>%
  mutate(year = as.factor(year)) %>%
  pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms')

ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  ggtitle('Max annual cumulative sums')

ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  #geom_point(aes(color = source)) +
  facet_wrap(~flow_type, scales = 'free') +
  ggtitle('Max annual cumulative sums')

### RD and RG by season

```{r flow season, echo = F, fig.width = 12, fig.asp = 0.75, out.width = "100%"}

#group by season and get max sums by season
flow_season <- gw %>%
  dplyr::select(RD1cumsum, RD2cumsum, RG1cumsum, RG2cumsum, date, year, source) %>%
  mutate(month = month(date)) %>%
  mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt',
                            month %in% c(7,8,9,10) ~ 'monsoon',
                            month %in% c(11,12,1,2) ~ 'baseflow')) %>%
  group_by(source, year, season) %>%
  summarize(yr_season_RD1 = max(RD1cumsum),
            yr_season_RD2 = max(RD2cumsum),
            yr_season_RG1 = max(RG1cumsum),
            yr_season_RG2 = max(RG2cumsum)) %>%
            pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'flow_cms')

flow_season %>%
  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  #geom_point(aes(color = source)) +
  facet_wrap(~season, scales = 'free') +
  ggtitle('Max annual season cumulative sums') +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(text = element_text(size = 20))

flow_season %>%
  ggplot(aes(x = flow_type, y = flow_cms, fill = source)) +
  geom_boxplot(position = position_dodge(1)) +
  geom_point(position=position_jitterdodge(),alpha=0.3) +
  #geom_point(aes(color = source)) +
  facet_wrap(~season + flow_type, scales = 'free') +
  ggtitle('Max annual season cumulative sums') +
  theme_bw() +
  theme(text = element_text(size = 20))

# HRU results

## Tmean difference

2011-2020 average of daily station-grid Tmean

```{r cumulative tmean for HRUs, echo = F}
#grid first
setwd(here("HRU_output/grid"))

read_ages_grid <- function(dataframe){
  read_csv(dataframe, skip = 3) %>%
  slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(time = ymd(time)) %>%
  mutate_if(is.character, as.numeric) %>%
  mutate(source = 'grid')

#pull in all filenames with HRU in the name
filenames <- list.files(".", pattern="HRU", full.names=F)

#read all the csvs using read_ages function
dataframes <- lapply(filenames, read_ages_grid)

#name all the csvs based on first 6 characters
names(dataframes) <- substr(filenames, 1, 6)

#bind all and make 1 df
hru_grids <- dataframes %>%
  bind_rows()

#statn next
setwd(here("HRU_output/statn"))

read_ages_statn <- function(dataframe){
  read_csv(dataframe, skip = 3) %>%
  slice(3:n()) %>%
  dplyr::select(-starts_with('@'),
                -1) %>%
  mutate(time = ymd(time)) %>%
  mutate_if(is.character, as.numeric) %>%
  mutate(source = 'statn')

#pull in all filenames with HRU in the name
filenames <- list.files(".", pattern="HRU", full.names=F)

#read all the csvs using read_ages function
dataframes <- lapply(filenames, read_ages_statn)

#name all the csvs based on first 6 characters
names(dataframes) <- substr(filenames, 1, 6)

#bind all and make 1 df
hru_statn <- dataframes %>%
  bind_rows()

#get rid of a bunch of data
hru_grid_tmean <- hru_grids %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_grid = tmean)  %>%
  group_by(ID) %>%
  summarize(tmean_all_grid = mean(tmean_grid))

hru_statn_tmean <- hru_statn %>%
  dplyr::select(c(time, ID, tmean)) %>%
  rename(tmean_statn = tmean) %>%
  group_by(ID) %>%
  summarize(tmean_all_statn = mean(tmean_statn))

tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>%
  mutate(diff = tmean_all_statn - tmean_all_grid) %>%
  rename(value = ID)

hrus_map_tmean <- left_join(hrus, tmean_hrus, by = 'value')

tmap_mode('view')

locations_t <- locations %>%
  dplyr::filter(name %in% c('Gordon_South', 'Gordon_North',
                        'Betasso', 'Niwot_Snotel',
                        'University Camp SNTL'))

tm_shape(hrus_map_tmean) +
  tm_polygons('diff', id = 'value',
              breaks = c(-6,-4,-2,0,2,4,6)) +
tm_shape(locations_t) +
  tm_symbols(col='blue', size=4)

## Tmax difference

```{r tmax, echo = F}

tmax_grid <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv'))%>%
  pivot_longer(cols = `3`:`19`,
               names_to = 'value',
               values_to = 'tmax_grid') %>%
  mutate(time = dmy(time)) %>%
  group_by(value) %>%
  summarize(Tmax_mean_grid = mean(tmax_grid))

tmax_statn <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>%
  pivot_longer(cols = `3`:`19`,
               names_to = 'value',
               values_to = 'tmax_statn') %>%
  mutate(time = dmy(time)) %>%
  group_by(value) %>%
  summarize(Tmax_mean_statn = mean(tmax_statn))

tmax_hrus <- left_join(tmax_grid, tmax_statn, by = c('value')) %>%
  mutate(diff = Tmax_mean_statn - Tmax_mean_grid,
         value = as.numeric(value))

hrus_map_tmax <- left_join(hrus, tmax_hrus, by = 'value')

tmap_mode('view')

tm_shape(hrus_map_tmax) +
  tm_polygons('diff', id = 'value',
              breaks = c(-6,-4,-2,0,2,4,6)) +
tm_shape(locations_t) +
  tm_symbols(col='blue', size=4)

## Tmax monthly average

```{r tmax month, echo = F}

tmax_grid_mo <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv')) %>%
  pivot_longer(cols = `3`:`19`,
               names_to = 'value',
               values_to = 'tmax_grid') %>%
  mutate(time = dmy(time),
         month = month(time)) %>%
  filter(month %in% c(3:6)) %>%
  group_by(value, month) %>%
  summarize(avg_tmax_grid = mean(tmax_grid))

tmax_statn_mo <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>%
  pivot_longer(cols = `3`:`19`,
               names_to = 'value',
               values_to = 'tmax_statn') %>%
  mutate(time = dmy(time),
         month = month(time)) %>%
  filter(month %in% c(3:6)) %>%
  group_by(value, month) %>%
  summarize(avg_tmax_statn = mean(tmax_statn))

tmax_hrus_mo <- left_join(tmax_grid_mo, tmax_statn_mo, by = c('value', 'month')) %>%
  mutate(mo_tmax_diff = avg_tmax_statn - avg_tmax_grid,
         value = as.numeric(value))

tmap_mode('plot')

#march
tmax_hrus_mar<- tmax_hrus_mo %>%
  filter(month == 3)

hrus_map_tmax_mar <- left_join(hrus, tmax_hrus_mar, by = 'value')

mar_tmax <- tm_shape(hrus_map_tmax_mar) +
  #tm_polygons('mo_tmax_diff', id = 'value') +
  tm_fill('mo_tmax_diff', id = 'value',
          breaks = c(-6,-4,-2,0,2,4,6)) +
  tm_borders() +
  tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'March avg tmax',
            legend.outside = T)

#april
tmax_hrus_apr<- tmax_hrus_mo %>%
  filter(month == 4)

hrus_map_tmax_apr <- left_join(hrus, tmax_hrus_apr, by = 'value')

apr_tmax <- tm_shape(hrus_map_tmax_apr) +
  tm_fill('mo_tmax_diff', id = 'value',
          breaks = c(-6,-4,-2,0,2,4,6)) +
  tm_borders() +
  tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'April avg tmax',
            legend.outside = T)

#may
tmax_hrus_may<- tmax_hrus_mo %>%
  filter(month == 5)

hrus_map_tmax_may <- left_join(hrus, tmax_hrus_may, by = 'value')

may_tmax <- tm_shape(hrus_map_tmax_may) +
  tm_fill('mo_tmax_diff', id = 'value',
         breaks = c(-6,-4,-2,0,2,4,6)) +
  tm_borders() +
tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'May avg tmax',
            legend.outside = T)

#june
tmax_hrus_jun<- tmax_hrus_mo %>%
  filter(month == 6)

hrus_map_tmax_jun <- left_join(hrus, tmax_hrus_jun, by = 'value')

jun_tmax <- tm_shape(hrus_map_tmax_jun) +
  tm_fill('mo_tmax_diff', id = 'value',
         breaks = c(-6,-4,-2,0,2,4,6)) +
  tm_borders() +
tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'June avg tmax',
            legend.outside = T)

tmap_arrange(mar_tmax, apr_tmax, may_tmax, jun_tmax)

## Tmin difference

```{r tmin, echo = F}

>>>>

```{r echo = FALSE, message = FALSE, warning = FALSE, include = F}

rm(statn_2011, statn_2012, statn_2013, statn_2014, statn_2015,
                  statn_2016, statn_2017, statn_2018, statn_2019, statn_2020,
                  statn_all., statn_all)

setwd("/Users/megansears/Documents/Repos/fourmile/38HRU_model/cals")

@@

name2 <- levels(burn_params$params)

lapply(name2, plot_burnparams)

@@

```{r hydrographs, echo = F}
setwd('/Users/megansears/Documents/Repos/fourmile/38HRU_model')

flow <- read_csv('discharge_all.csv') %>%
  replace(.==-9999, NA) %>%
  rename(date = time) %>%
  mutate(date = mdy(date))

@@

q_ensemble <- ggplot(ensem_pivot, aes(date, q_m3s, color = cal_run)) +
  geom_line() +
  scale_color_manual(name="cal_run", values=c('obs'='black',
                                            "grid_ensemble"="maroon",
                                            "statn_ensemble"="darkturquoise",
                                            "grid_all"="purple1",
                                            "statn_all"='springgreen4',
                                            "all_ensemble" = "orange")) +
  scale_y_continuous(name = 'Q_m3s') +
  theme_bw()

q_ensemble

@@

<!-- # Catchment results -->

<!-- ## Precip -->

<!-- ```{r catch precip, echo = F} -->
<!-- setwd("/Users/megansears/Documents/Repos/fourmile/catchment_output") -->

<!-- statn <- read_csv('statnall.csv') -->
<!-- grid <- read_csv('gridall.csv') -->

<!-- grid <- grid %>% mutate(site = 'grid') -->
<!-- statn <- statn %>% mutate(site = 'statn') -->

<!-- catchment <- bind_rows(grid, statn) %>% -->
<!--   mutate(year = as.factor(year(time))) %>% -->
<!--   group_by(year, site) %>% -->
<!--   mutate(cumulative_p = cumsum(precip)) -->

<!-- #plot cumulative precip by year -->
<!-- plot_cumprecip <- function(calyear) { -->
<!--   {catchment %>% -->
<!--     filter(year == calyear) %>% -->
<!--     ggplot(aes(x = time, -->
<!--                y = cumulative_p, color = site)) + -->
<!--     geom_line(size=1) + -->
<!--     ggtitle(calyear) + -->
<!--     ylab('Cumulative precip (mm)') + -->
<!--     theme_bw() + -->
<!--     theme(axis.text.x = element_text(angle = 45, hjust=1))} %>% -->
<!--     ggplotly() -->
<!-- } -->

<!-- name <- levels(catchment$year) -->

<!-- precip_plots <- lapply(name, plot_cumprecip) -->

<!-- htmltools::tagList(precip_plots) -->

<!-- precip_plots -->

<!-- ## total P -->
<!-- max_cumulativep <- catchment %>% -->
<!--   group_by(year, site) %>% -->
<!--   summarize(total_cumulativep = max(cumulative_p)) -->

<!-- ggplot(max_cumulativep, aes(x=year, y=total_cumulativep, color=site)) + -->
<!--   geom_point(size=3) + -->
<!--   ggtitle('Total cumulative precip (mm) by year') -->

<!-- ``` -->

<!-- ## Tmean -->

<!-- ```{r tmean catch, echo = F} -->
<!-- ## tmean -->
<!-- tmean <- catchment %>% -->
<!--   group_by(year, site) %>% -->
<!--   summarize(tmean = mean(tmean)) %>% -->
<!--   ggplot(aes(x = year, y=tmean, color = site)) + -->
<!--   geom_point(size=3) + -->
<!--   ggtitle('Average temp by year') -->

<!-- tmean -->

<!-- ``` -->

<!-- ## RD and RG -->

<!-- ```{r rd and rg, echo = F, fig.width = 14, fig.asp = 1, out.width = "100%"} -->

<!-- gw_grid <- read_csv(here('catchment_output/gridall_outlet.csv')) %>% -->
<!--   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
<!--   mutate(source = 'grid') -->

<!-- gw_statn <- read_csv(here('catchment_output/statnall_outlet.csv')) %>% -->
<!--   dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>% -->
<!--   mutate(source = 'statn') -->

<!-- gw <- bind_rows(gw_grid, gw_statn) %>% -->
<!--   mutate(year = year(time)) %>% -->
<!--   rename(date = time) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=catchmentRD1_w), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('RD1') + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=catchmentRD2_w), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('RD2') + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=catchmentRG1_w), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('RG1') + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=catchmentRG2_w), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('RG2') + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- gw <- gw %>% -->
<!--   group_by(year, source) %>% -->
<!--   mutate(RD1cumsum = cumsum(catchmentRD1_w), -->
<!--          RD2cumsum = cumsum(catchmentRD2_w), -->
<!--          RG1cumsum = cumsum(catchmentRG1_w), -->
<!--          RG2cumsum = cumsum(catchmentRG2_w)) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=RD1cumsum), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('Cumulative RD1') + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=RD2cumsum), size = 1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol=2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('Cumulative RD2') + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=RG1cumsum), size  = 1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('Cumulative RG1') + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- ggplot(gw, aes(x=date, color = source)) + -->
<!--   geom_line(aes(y=RG2cumsum), size =1) + -->
<!--   facet_wrap(~year, scales = 'free', ncol = 2) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   ggtitle('Cumulative RG2') + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- ``` -->

<!-- ```{r rd and rg sums, echo = F, fig.width = 22, fig.asp = 1.5, out.width = "100%"} -->

<!-- ################## -->
<!-- # all 4 with facets -->

<!-- ggplot(gw, aes(x=date)) + -->
<!--   geom_line(aes(y=RG2cumsum, color = 'cumulative RG2'), size =1) + -->
<!--   geom_line(aes(y=RG1cumsum, color = 'cumulative RG1'), size =1) + -->
<!--   geom_line(aes(y=RD1cumsum, color = 'cumulative RD1'), size =1) + -->
<!--   geom_line(aes(y=RD2cumsum, color = 'cumulative RD2'), size =1) + -->
<!--   scale_x_date(labels = date_format("%b")) + -->
<!--   facet_wrap(~year + source, scales = 'free_x', ncol=2) + -->
<!--   ggtitle('Cumulative RD and RG') + -->
<!--   theme(text = element_text(size = 24)) -->

<!-- ``` -->

<!-- ```{r gw boxplot, echo = F} -->

<!-- gw_maxcumsum <- gw %>% -->
<!--   group_by(source, year) %>% -->
<!--   summarize(yr_max_RD1 = max(RD1cumsum), -->
<!--             yr_max_RD2 = max(RD2cumsum), -->
<!--             yr_max_RG1 = max(RG1cumsum), -->
<!--             yr_max_RG2 = max(RG2cumsum)) %>% -->
<!--   mutate(year = as.factor(year)) %>% -->
<!--   pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms') -->

<!-- ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) + -->
<!--   geom_boxplot(position = position_dodge(1)) + -->
<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
<!--   ggtitle('Max annual cumulative sums') -->

<!-- ggplot(gw_maxcumsum, aes(x = flow_type, y = flow_cms, fill = source)) + -->
<!--   geom_boxplot(position = position_dodge(1)) + -->
<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
<!--   #geom_point(aes(color = source)) + -->
<!--   facet_wrap(~flow_type, scales = 'free') + -->
<!--   ggtitle('Max annual cumulative sums') -->

<!-- ``` -->

<!-- ### RD and RG by season -->

<!-- ```{r flow season, echo = F, fig.width = 12, fig.asp = 0.75, out.width = "100%"} -->

<!-- #group by season and get max sums by season -->
<!-- flow_season <- gw %>% -->
<!--   dplyr::select(RD1cumsum, RD2cumsum, RG1cumsum, RG2cumsum, date, year, source) %>% -->
<!--   mutate(month = month(date)) %>% -->
<!--   mutate(season = case_when(month %in% c(3,4,5,6) ~ 'snowmelt', -->
<!--                             month %in% c(7,8,9,10) ~ 'monsoon', -->
<!--                             month %in% c(11,12,1,2) ~ 'baseflow')) %>% -->
<!--   group_by(source, year, season) %>% -->
<!--   summarize(yr_season_RD1 = max(RD1cumsum), -->
<!--             yr_season_RD2 = max(RD2cumsum), -->
<!--             yr_season_RG1 = max(RG1cumsum), -->
<!--             yr_season_RG2 = max(RG2cumsum)) %>% -->
<!--             pivot_longer(!c(year, source, season), names_to = 'flow_type', values_to = 'flow_cms') -->

<!-- flow_season %>% -->
<!--   ggplot(aes(x = flow_type, y = flow_cms, fill = source)) + -->
<!--   geom_boxplot(position = position_dodge(1)) + -->
<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
<!--   #geom_point(aes(color = source)) + -->
<!--   facet_wrap(~season, scales = 'free') + -->
<!--   ggtitle('Max annual season cumulative sums') + -->
<!--   theme_bw() + -->
<!--   theme(axis.text.x = element_text(angle = 45, hjust = 1)) + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- flow_season %>% -->
<!--   ggplot(aes(x = flow_type, y = flow_cms, fill = source)) + -->
<!--   geom_boxplot(position = position_dodge(1)) + -->
<!--   geom_point(position=position_jitterdodge(),alpha=0.3) + -->
<!--   #geom_point(aes(color = source)) + -->
<!--   facet_wrap(~season + flow_type, scales = 'free') + -->
<!--   ggtitle('Max annual season cumulative sums') + -->
<!--   theme_bw() + -->
<!--   theme(text = element_text(size = 20)) -->

<!-- ``` -->

<!-- # HRU results -->

<!-- ## Tmean difference -->

<!-- 2011-2020 average of daily station-grid Tmean -->

<!-- ```{r cumulative tmean for HRUs, echo = F} -->
<!-- #grid first -->
<!-- setwd(here("HRU_output/grid")) -->

<!-- read_ages_grid <- function(dataframe){ -->
<!--   read_csv(dataframe, skip = 3) %>% -->
<!--   slice(3:n()) %>% -->
<!--   dplyr::select(-starts_with('@'), -->
<!--                 -1) %>% -->
<!--   mutate(time = ymd(time)) %>% -->
<!--   mutate_if(is.character, as.numeric) %>% -->
<!--   mutate(source = 'grid') -->

<!-- } -->

<!-- #pull in all filenames with HRU in the name -->
<!-- filenames <- list.files(".", pattern="HRU", full.names=F) -->

<!-- #read all the csvs using read_ages function -->
<!-- dataframes <- lapply(filenames, read_ages_grid) -->

<!-- #name all the csvs based on first 6 characters -->
<!-- names(dataframes) <- substr(filenames, 1, 6) -->

<!-- #bind all and make 1 df -->
<!-- hru_grids <- dataframes %>% -->
<!--   bind_rows() -->

<!-- #statn next -->
<!-- setwd(here("HRU_output/statn")) -->

<!-- read_ages_statn <- function(dataframe){ -->
<!--   read_csv(dataframe, skip = 3) %>% -->
<!--   slice(3:n()) %>% -->
<!--   dplyr::select(-starts_with('@'), -->
<!--                 -1) %>% -->
<!--   mutate(time = ymd(time)) %>% -->
<!--   mutate_if(is.character, as.numeric) %>% -->
<!--   mutate(source = 'statn') -->

<!-- } -->

<!-- #pull in all filenames with HRU in the name -->
<!-- filenames <- list.files(".", pattern="HRU", full.names=F) -->

<!-- #read all the csvs using read_ages function -->
<!-- dataframes <- lapply(filenames, read_ages_statn) -->

<!-- #name all the csvs based on first 6 characters -->
<!-- names(dataframes) <- substr(filenames, 1, 6) -->

<!-- #bind all and make 1 df -->
<!-- hru_statn <- dataframes %>% -->
<!--   bind_rows() -->

<!-- #get rid of a bunch of data -->
<!-- hru_grid_tmean <- hru_grids %>% -->
<!--   dplyr::select(c(time, ID, tmean)) %>% -->
<!--   rename(tmean_grid = tmean)  %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(tmean_all_grid = mean(tmean_grid)) -->

<!-- hru_statn_tmean <- hru_statn %>% -->
<!--   dplyr::select(c(time, ID, tmean)) %>% -->
<!--   rename(tmean_statn = tmean) %>% -->
<!--   group_by(ID) %>% -->
<!--   summarize(tmean_all_statn = mean(tmean_statn)) -->

<!-- tmean_hrus <- left_join(hru_grid_tmean, hru_statn_tmean, by = c('ID')) %>% -->
<!--   mutate(diff = tmean_all_statn - tmean_all_grid) %>% -->
<!--   rename(value = ID) -->

<!-- hrus_map_tmean <- left_join(hrus, tmean_hrus, by = 'value') -->

<!-- tmap_mode('view') -->

<!-- locations_t <- locations %>% -->
<!--   dplyr::filter(name %in% c('Gordon_South', 'Gordon_North', -->
<!--                         'Betasso', 'Niwot_Snotel', -->
<!--                         'University Camp SNTL')) -->

<!-- tm_shape(hrus_map_tmean) + -->
<!--   tm_polygons('diff', id = 'value', -->
<!--               breaks = c(-6,-4,-2,0,2,4,6)) + -->
<!-- tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size=4) -->

<!-- ``` -->

<!-- ## Tmax difference -->

<!-- ```{r tmax, echo = F} -->

<!-- tmax_grid <- read_csv(here('HRU_output/reg_tmaxAll_prism.csv'))%>% -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value', -->
<!--                values_to = 'tmax_grid') %>% -->
<!--   mutate(time = dmy(time)) %>% -->
<!--   group_by(value) %>% -->
<!--   summarize(Tmax_mean_grid = mean(tmax_grid)) -->

<!-- tmax_statn <- read_csv(here('HRU_output/reg_tmaxAll.csv')) %>% -->
<!--   pivot_longer(cols = `3`:`19`, -->
<!--                names_to = 'value', -->
<!--                values_to = 'tmax_statn') %>% -->
<!--   mutate(time = dmy(time)) %>% -->
<!--   group_by(value) %>% -->
<!--   summarize(Tmax_mean_statn = mean(tmax_statn)) -->

<!-- tmax_hrus <- left_join(tmax_grid, tmax_statn, by = c('value')) %>% -->
<!--   mutate(diff = Tmax_mean_statn - Tmax_mean_grid, -->
<!--          value = as.numeric(value)) -->

<!-- hrus_map_tmax <- left_join(hrus, tmax_hrus, by = 'value') -->

<!-- tmap_mode('view') -->

<!-- tm_shape(hrus_map_tmax) + -->
<!--   tm_polygons('diff', id = 'value', -->
<!--               breaks = c(-6,-4,-2,0,2,4,6)) + -->
<!-- tm_shape(locations_t) + -->
<!--   tm_symbols(col='blue', size=4) -->

<!-- ``` -->

<!-- ## Tmax monthly average -->

<!-- ```{r tmax month, echo = F} -->
